Advantages of mixed quantum channels for information processing

### 2019-03-04 decorrelation/mixed_unitaries.tex
Edits from discussion

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
\newcommand{\error}{\ensuremath{{\mathcal{E}}}}
\def\id{\mbox{\small 1} \!\! \mbox{1}}

@@

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mixed quantum channels}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can model their action with completely positive, trace-preserving (CPTP) maps. These maps have a number of useful representations, including as Kraus operators[], Choi matrices[], and Jamiolkowsi states[]. But for the purposes of this article, \emph{process matrices} will be most convenient. The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the denity matrix. \note{Write some more...}

it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.  We can then represent the action of a CPTP map using a \emph{process matrix}, which acts on a vectorized quantum state by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
\end{equation}
Here $\actual$ is the actual gate as implemented, $\target$ is the target operation, and $\error$ is the effective error channel:
\begin{equation}\label{eq:process_matrix}
\error =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.  The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping. If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate. Any such Pauli error is expressible as a unitary matrix $U$ that acts on the density matrix by conjugation, and has an action on the vectorized density matrix given by: 
\begin{equation}
\vec{\rho}\rightarrow \rho_i\vec{\Sigma}_{ijk}U^{\dagger}_{kl}\vec{\Sigma}_{lmn}U_{mj}\end{equation}
 If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$). For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.

@@

Alternatively, we might consider eliminating off-diagonal entries of G:
\begin{equation}
	\left(\begin{array}{@{}ccccc@{}}
		0 & 0 & 0 & 0 \\ 
  		\cline{3-4}
    	0 & 0 & \multicolumn{1}{|c}{-1} & \multicolumn{1}{c|}{0} \\
    	\cline{3-3}		
		0 & 1 & 0 & \multicolumn{1}{|c|}{0}\\
		\cline{4-4}	
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
 resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable problem. In the case of a single qubit, it is clear that our generator is expressible as $\hat{n}\cdot\vec{\Sigma}$, where $\vec{\Sigma}$ is again the vector of Pauli operators. The condition that the off-diagonal terms vanish is then again the same condition that the origin lies in the convex hull of the vectors $\vec{n}_i$ for each $G_i$.
 \note{more here about alternative method. Also discuss Fig 2.}.

@@

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\note{write an introduction to this section here} 
In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors. These vectors might represent the off-diagonal elements of the error maps, or they could be the error generator. As we'll see in section ... we could also include the derivatives with respect to various parameters. With appropriate weighting, we could minimize any number of effects. Which optimization we choose will depend on the approach. \note{Then go into examples below. }

% ==============================================================================
% Section: Generators
% ==============================================================================

\subsection{First-order generators} % (fold)
\label{sub:first_order_generators}
\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MQC with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MQC with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

\subsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}

% subsection off_diagonals (end)

% ==============================================================================
% Section: Robustness
% ==============================================================================

\subsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
\note{this section is a little bit heavy on the notation - is there anything we can do to ease that? Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MQC will degrade. Thus, we would like to design MQCs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed quantum channel is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MQC}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MQC as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
\begin{equation}\label{eq:MQC-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.

@@

\subsection{Hamiltonian Norm Regularization}
\label{sec:norm}
While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution. In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}. To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:

@@

\subsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$. However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
\newcommand{\error}{\ensuremath{{\mathcal{E}}}}
\newcommand{\generator}{\ensuremath{{\mathsf{G}}}}
\def\id{\mbox{\small 1} \!\! \mbox{1}}

@@

\note{don't define diamond norm here}

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mixed quantum channels}
\label{sec:representing_quantum_gates}
\begin{enumerate}
	\item Specify the process matrix representation of a quantum channel in terms of the generalized Bloch vector
	\item 
\end{enumerate}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can model their action with completely positive, trace-preserving (CPTP) maps. These maps have a number of useful representations, including as Kraus operators[], Choi matrices[], and Jamiolkowsi states[]. But for the purposes of this article, \emph{process matrices} will be most convenient. The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the system density matrix. \note{Write some more...}
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
\end{equation}
We vectorize the density matrix as
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.  We can then represent the action of a CPTP map using a \emph{process matrix}, which acts on a vectorized quantum state by the usual matrix multiplication:

An important consequence of the linearity of this representation is that classical randomness can be easily encoded in the density matrix. Suppose that each time a gate is implemented, a different version of the gate is applied at random.

Here $\actual$ is the actual gate as implemented, $\target$ is the target operation, and $\error$ is the effective error channel:
\begin{equation}\label{eq:process_matrix}
\error =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.  The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping. If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate. Any such Pauli error is expressible as a unitary matrix $U$ that acts on the density matrix by conjugation, and has an action on the vectorized density matrix given by: 
\begin{equation}
\vec{\rho}\rightarrow \rho_i\vec{\Sigma}_{ijk}U^{\dagger}_{kl}\vec{\Sigma}_{lmn}U_{mj}\end{equation}
 If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$). For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.

@@

Alternatively, we might consider eliminating off-diagonal entries of $\error(\epsilon)$ \note{fix this}:
\begin{equation}
	\left(\begin{array}{@{}ccccc@{}}
		0 & 0 & 0 & 0 \\ 
  		\cline{3-4}
    	0 & 0 & \multicolumn{1}{|c}{-1} & \multicolumn{1}{c|}{0} \\
    	\cline{3-3}		
		0 & 1 & 0 & \multicolumn{1}{|c|}{0}\\
		\cline{4-4}	
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
 resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable problem. In the case of a single qubit, it is clear that our generator is expressible as $\hat{n}\cdot\vec{\Sigma}$, where $\vec{\Sigma}$ is again the vector of Pauli operators. The condition that the off-diagonal terms vanish is then again the same condition that the origin lies in the convex hull of the vectors $\vec{n}_i$ for each $G_i$.
 \note{more here about alternative method. Also discuss Fig 2.}.

@@

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\note{write an introduction to this section here, change notation to be consistent with other sections} 
In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors. These vectors might represent the off-diagonal elements of the error maps, or they could be the error generator. As we'll see in section ... we could also include the derivatives with respect to various parameters. With appropriate weighting, we could minimize any number of effects. Which optimization we choose will depend on the approach. \note{Then go into examples below. }

% ==============================================================================
% Section: Generators
% ==============================================================================
\subsection{Optimization Targets}
\subsubsection{First-order generators} % (fold)
\label{sub:first_order_generators}
\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MQC with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MQC with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

\subsubsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}
\note{write this section to basically discuss the original optimization problem (from years ago)}
% subsection off_diagonals (end)

% ==============================================================================
% Section: Robustness
% ==============================================================================
\subsection{Additional Constraints}
\subsubsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
\note{ Try to make this more readable }
While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MQC will degrade. Thus, we would like to design MQCs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed quantum channel is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MQC}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MQC as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
\begin{equation}\label{eq:MQC-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.

@@

\subsubsection{Hamiltonian Norm Regularization}
\label{sec:norm}
While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution. In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}. To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:

@@

\subsubsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$. However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
